Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-13 sections/correlated-sicm-and-srfm.tex
commented the last paragraph, is included in the first one

As mentioned in section~\ref{sec:correlating-sicm-and-fm}, SICM was also successfully combined 
with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015a}. The difference to the 
SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
fluorescently labeled molecules -- ATTO 655-phalloidin -- into living U2OS cells.

>>>>

% As mentioned in section~\ref{sec:correlating-sicm-and-fm}, SICM was also successfully combined 
% with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015a}. The difference to the 
% SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
% fluorescently labeled molecules -- ATTO 655-phalloidin -- into living U2OS cells.
